% !TEX program = xelatex
\documentclass[]{font}
\usepackage{fancyhdr}

\pagecolor{white}
\newcommand{\white}[1]{\textcolor{white}{\fontsize{1}{1.2}\selectfont{#1}}}

\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Mohammed}{Nisham}{ 
\urlstyle{same}\href{http://github.com/moonblade}{github.com/moonblade}| \href{https://www.linkedin.com/in/mnishamk}{linkedin.com/in/mnishamk}\\
\href{mailto:mnishamk@gmail.com}{mnishamk@gmail.com} | +91 9497267385
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Proficient:}
Kubernetes \textbullet{} 
Helm \textbullet{} 
Argo CD \textbullet{} 
Kustomize \textbullet{} 
Terraform \textbullet{} 
JavaScript \textbullet{} 
Angular \textbullet{} 
React \textbullet{}
Express \textbullet{}  
Mongo \textbullet{} 
Python \textbullet{}
Java \textbullet{} 
Shell \textbullet{} 
% Typescript \textbullet{}

\location{Familiar :}
Android \textbullet{} 
SQL \textbullet{} 
Elasticsearch \textbullet{}
PHP \textbullet{}
\LaTeX \textbullet{} 
C++ \textbullet{}
\sectionsep

% \subsection{Soft skills}
% Initiative \textbullet{} Leadership \\
% Communication 
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Achievements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements} 
\vspace{\topsep}
\textbullet{} Certified Kubernetes Administrator - LF-l6mags4tc3 \\
\textbullet{} Completed Stanford university \href{https://www.coursera.org/account/accomplishments/records/EJQWCKEBUSBD}{Machine Learning course} from Coursera \\
% \textbullet{} First Place, Game design workshop, IEEE KiTeS - 2015 \\
% \textbullet{} First Place, Firefox Appday, application development competition, Barton Hill, Trivandrum - 2015 \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{College of Engg. TVM}
\descript{B. Tech in Computer Science}
\location{July 2017 | Trivandrum}
\sectionsep

\subsection{Kendriya Vidyalaya}
\location{Grad. May 2011 | Kozhikode}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\white{\texttt{Hey robot, Here's my skill list. JavaScript angular angularjs react MEAN MERN mongo node express python shell java c++ elasticsearch devops docker kubernetes eks helm ci cd gitlab }}
\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Freiheit.com technologies}
\descript{| Site Reliability Engineer}
\location{May 2022 - Present | Hamburg, Germany}

Kubernetes, ArgoCD, Kuberpult, Github actions, Golang, Helm, GCP
\vspace{\topsep}

\begin{tightemize}
\item Created execution plan tool which identifies services to build, based on changed files and their dependency trees, and creates a plan to build them in order. 
\item Ported existing CI from Jenkins to Github Actions using the new execution plan
\end{tightemize}
\sectionsep

\runsubsection{Freelance}
% \runsubsection{Dersalvador}
\descript{| Devops Engineer}
\location{June 2020 - December 2021 | Remote}

Kubernetes, Argo CD, Docker, Gitlab CI/CD, Helm, EKS
\vspace{\topsep}

% \textbf{BROKERME}:
% \vspace{\topsep}

\begin{tightemize}
\item Development and devops work, A freelancer portal where registered users may apply for relevant job offers from participating agencies.
\item App is composed of multiple microservices, each on a seperate k8s pod. Setup includes helm chart for different environments. Deployed on two GCP clusters.
\item Setup self managed Argo CD server, synced with git repository for maintaining a sub application.
\item Deployment of microservices into multiple environments integrated into gitlab CI/CD
\item Optimized gitlab pipeline to run microservice build and test stages in parallel
% \item Added Ingress routes for newer microservices
% \item Built selenium UI testsuite from scratch running on Browserstack
\end{tightemize}

% \vspace{\topsep}
% \textbf{EBMPAPST}:

% \begin{tightemize}
% \item Created scripts to setup an amazon EKS cluster from scratch and give permission to the cluster to required IAM entities.
% \item Provided scripts to Deploy docker containers to pods within the cluster in a user namespace via Helm charts
% % \item Setup Ingress for access to the deployed app 
% \item Integrated deployment stage into existing gitlab CI/CD pipeline
% \end{tightemize}
\sectionsep

\runsubsection{Commvault}
\descript{| Senior Engineer II }
\location{Jul 2017 - April 2022 | Bengaluru, India}
Kubernetes, Angular, Java, Python, React
\vspace{\topsep}
\begin{tightemize}
\item Initial phase of containerizing existing services, setup kubernetes environment and deployed webserver microservice on it
\item Setup ArgoCD environment for GitOps delivery of microservices, along with loki and prometheus for logging
\item Setup Tekton pipelines for updating GitOps repositories based on webhook trigger
\item Lead developer for global admin console, enabling users to aggregate and maintain data from multiple CommServers without switching overhead. 
% \item Redesigned backup view component as a calendar UI increasing customer interaction with the element.
% \item Involved in the initial phase for shift of frontend UI codebase from angularJS to react.
% \item Design and implementation of subsystems from Java GUI into command center enhancing ease of use.
% \item Created search feature in Java GUI to enable faster client creation enhancing user experience.
% \item Provided organization feature in Java GUI with modified dialogs providing consistency with web UI.
% \item Tracking and fixing customer issues related to search, backup and install software features.
% \item Design of frontend UI with proper REST calls for functionality.
% \item Added toggling of custom alerts based on customer requirement.
\item Automated install and update of commvault software on remote machine with python scripts decreasing turnaround time.
\item Developed python scripts for automated sandbox creation and form building increasing throughput. 
\item Implemented auto tracking of work items via Trello API for easier overview.
% \item Automated logging and mailing of work processes completed over the week for easier accessibility.
\end{tightemize}    
\sectionsep

% \runsubsection{Sensomate Systems}
% \descript{| Developer Intern }
% \location{2015 - 2016 | Trivandrum}
% Android, AngularJs 
% % \vspace{\topsep}
% \begin{tightemize}
% \item Indoor navigation system in hospitals. Includes android app for navigation and an AngularJs admin panel.
% \end{tightemize}    
% \sectionsep

% \runsubsection{Freelancer}
% \descript{| Web Developer }
% % \location{2015 - 2019}
% Angular, React, Express, Kubernetes, Elasticsearch
% % \vspace{\topsep}
% \begin{tightemize}
% \item Developed a freelancer portal where registered users are forwarded relevant job offers from participating agencies. 
% Currently in Beta.
% \item Elasticsearch based search engine for legal documents supporting search operators.
% \item An angularJs web portal for tax calculations.
% \end{tightemize}    


\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Personal projects}

\runsubsection{\href{https://github.com/moonblade/Microservice-Assessment}{Watermark microservices project}}
\location{ 2020 }
Asynchronous event-driven cloud native app created to learn microservices and kubernetes, deployed on a kind cluster.
\sectionsep

\runsubsection{\href{https://github.com/moonblade/gunt}{Online easter egg hunt}}
\location{ 2016 }
Designed and developed a game, inspired by the book Ready Player One. Spanning the internet, involving puzzles, rhymes and cryptography.
\sectionsep

% \runsubsection{Eye Pencil}
% \location{ 2015 }
% An iris tracker built into a spectacle frame coupled with a keyboard on screen. Enables paraplegic patients to type out their intentions with eye movements. Uses opencv image processing. Won best innovation award at college expo.
% \sectionsep

% \runsubsection{\href{http://forum.xda-developers.com/showthread.php?t=2276871}{Rom Porter Tool}}
% \location{ 2013 }
% A windows batch tool to automatically ports ROMs from one andriod device to another with minimal input. 25K+ downloads.
% \sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
