\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\usepackage{tabularx}
\usepackage[english,num]{isodate}
\usepackage{lipsum}

% \isodate
\isodash{-}

\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{\uppercase{#1} \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
\newcommand{\when}[1]{\hfill \textbf{#1}} 

\newenvironment{noSepItemize}
{ \begin{itemize}
    \setlength{\itemsep}{0pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}     }
{ \end{itemize}                  }
%-----------------------------------------------------------


\begin{document}
\hspace{0.5cm}\\[-0.2cm]

\begin{center}
\textbf{\Large{Mohammed Nisham K}} \\
mnishamk1995@gmail.com \textbullet\, +91 9497267385 \textbullet\, \href{https://in.linkedin.com/in/mnishamk}{https://in.linkedin.com/in/mnishamk}\\
Sarayi, Near Indian Express, West Hill, Kozhikkode \\
\end{center}

\resheading{\textbf{ACADEMIC DETAILS} }\\[\lsep]
\\ \\
%\begin{table}[ht!]
%\begin{center}
\indent \begin{tabular}{ l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l }
% \hline
\textbf{Examination} & \textbf{University} & \textbf{Institute} & \textbf{Year} & \textbf{GPA/\%} \\
% \hline
Class X & CBSE & Kendriya Vidyalaya, Kozhikkode & 2011 & 9.5 \\
Class XII & CBSE & Kendriya Vidyalaya, Kozhikkode & 2013 & 93\% \\
% UnderGraduate Specialization: & \textit{Computer Engineering} \\
B.Tech Computer Science & Kerala University & College of Engineering Trivandrum & 2017 & 8.74 (Till S4)\\
% and Engineering\\
% \hline
\end{tabular}
%\end{center}
%\end{table}
\\ \\

\resheading{\textbf{Experience} }\\[\lsep]
\begin{itemize}
\item \noindent \textbf{Developer Internship, Sensomate Systems} \when{2015}\\
	\indent Development and debugging team. Projects include \textbf{BLE based navigation system} for android, an \textbf{ionic webapp}, other \textbf{Angular JS} frontend works
\item \noindent \textbf{Freelance Developer, freelancer.com} \when{2015 - 16}\\
	\indent \textbf{Elastic search} based search engine for legal documents, Angular JS Tax Calculator, other Android and Angular works
\end{itemize}

\resheading{\textbf{TECHNICAL SKILLS} }\\[\lsep]
\begin{itemize}
\item \noindent \textbf{Languages} (C, C++, Java),\, \textbf{Database} (MySQL, Mongo),\, \textbf{Script} (Python, Shell),\, \textbf{Web} (HTML, Javascript, PHP, AngularJS, MEAN stack),\, \textbf{Tools} (Android Studio, Netbeans, Unity, \LaTeX).
\end{itemize}

\resheading{\textbf{PROJECTS} }\\[\lsep]
% \begin{itemize}
\begin{noSepItemize}
\item \textbf{Elastic Search Legal Database} \when{2016-Present}\\
	A search engine in for a unified database of legal cases in India, with Elastic Search and Angular JS front End.
\item \textbf{BLE Navigation System} \when{2015-Present}\\
	An android app for indoor navigation using Bluetooth low energy Beacons. Phase 1 Complete. To be deployed in KIMS hospital.
\item \textbf{IEEE Link App} \when{2015}\\
	An app to serve as a unified publicity platform for IEEE LINK(Local Integrated Network of Kerala IEEE Students). Phase 1 was revealed at Kerala IEEE Technical Symposium (KITeS) '15.
\item \textbf{Eye Pencil} \when{2015}\\
	An Eye tracker built into a spectacle frame coupled with a keyboard on screen. Enabling 
paraplegic or TBI patient to type his intentions on the screen. Won best Innovation award at cetex expo.
\item \textbf{Rom Porter Tool} \when{2012}\\
	A windows batch tool to port android roms with minimum user input, 10K+ downloads.
% \end{itemize}
\end{noSepItemize}

\resheading{\textbf{Achievements} }\\[\lsep]
\begin{noSepItemize}
	\item \noindent Completed Stanford university \textbf{\href{https://www.coursera.org/account/accomplishments/records/EJQWCKEBUSBD}{Machine Learning course}} from Coursera\when{2016}
	\item \noindent First Place, \textbf{Game design} workshop, IEEE KiTeS \when{2015}
	\item \noindent First Place, Firefox Appday, application development competition, Barton Hill, Trivandrum \when{2015}
	\item \noindent Third Place, Cloud computing workshop, NSS Palakkad \when{2014}
\end{noSepItemize}

\resheading{\textbf{Volunteering Experience} }\\[\lsep]
\begin{noSepItemize}
	\item \noindent Conducted Robotics Project Expo at Pankajakasthuri College\when{2014}
	\item \noindent Head of Android Student Club, CET \when{2015}
	\item \noindent Conducted various Android related workshops, competitions for juniors\when{2014 - 15}
	\item \noindent Development mentor at Ignite women's hackathon \when{2015}
\end{noSepItemize}

\resheading{\textbf{Professional Membership} }\\[\lsep]
\begin{noSepItemize}
	\item \noindent \textbf{IEEE} \when{2014-Present}
	\item \noindent \textbf{IEEE Computer Society} \when{2014-Present}
\end{noSepItemize}

\end{document}

